---
title: "LeCroy Geodata Help"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- For the source of this file, see  https://github.com/bbest/lecroy-geodata/blob/master/docs/index.Rmd.

## Original

Sorry - here is essentially what I do. There are no error messages since it runs, but the result is incorrect because all points are shown as being a single point within a single polygon.
The coordinates are different and that is likely the issue but I can't figure out how to correct it. The bounding boxes show this:

```
shapefile_util@bbox
        min      max
x -374446.5 540037.5
y -604489.9 450020.7

v_comp@bbox
           min        max
lon -124.17578 -115.55391
lat   32.54582   40.80654
```

## Setup Libraries and Paths

```{r}
library(tidyverse)
library(sp)
library(spatialEco)
library(maptools)

# set paths
dir_data      <- "~/Dropbox/CA util" # change this for your machine
vouchers_csv  <- file.path(dir_data, "vouchers_subset.csv")
utilities_shp <- file.path(
  dir_data,
  "UtilityShapefile/California_Electric_Utility_Service_Territory_.shp")

#import voucher data
vouchers_df <- read_csv(vouchers_csv)
```

## Old School `sp`, `maptools` functions

```{r}
#convert points to spatialpointsdataframe 
vouchers_pt <- SpatialPointsDataFrame(
  vouchers_df[, 15:16],
  vouchers_df[, 1:22],
  proj4string = CRS("+proj=longlat +datum=WGS84"))

vouchers_pt@bbox

#Import shapefile of counties
utilities_ply <- readShapeSpatial(
  utilities_shp, 
  proj4string = CRS( "+proj=longlat +datum=WGS84"))

utilities_ply@bbox

#Match data with utility  polygons
vouchers_in_utilities_pt <- point.in.poly(vouchers_pt, utilities_ply)
head(vouchers_in_utilities_pt)
```

## The Problem: using deprecated `maptools::readShapeSpatial()`

Per the documentation accessed from the R Console via `?readShapeSpatial` or online at [readShapeSpatial function | R Documentation](https://www.rdocumentation.org/packages/maptools/versions/0.9-4/topics/readShapeSpatial), you're using the **deprecated** function  `maptools::readShapeSpatial()` that does not read in the spatial projection information. Per documentation you should use `rgdal::readOGR()` or better yet `sf::st_read()`:

> The use of this function is deprecated and it is not being maintained. Use rgdal::readOGR() or sf::st_read() instead - both of these read the coordinate reference system from the input file, while this deprecated function does not. For writing, use rgdal::writeOGR() or sf::st_write() instead.

Most significantly, this function doesn't properly read the coordinate reference system and manually setting it doesn't transform it.


```{r}
rgdal::ogrInfo(utilities_shp)
```

## New School `sf` functions

```{r}
library(sf)

vouchers_pt <- st_as_sf(vouchers_df, coords = c("lon", "lat"), crs = 4326)
vouchers_pt

#Import shapefile of counties
utilities_ply <- read_sf(utilities_shp)
utilities_ply
  
utilities_ply <- read_sf(utilities_shp) %>% 
  st_transform(crs = 4326)
utilities_ply

vouchers_in_utilities_pt <- st_join(
  vouchers_pt, utilities_ply, join = st_intersects)
vouchers_in_utilities_pt
```

## Next time

- Read documentation on functions

- Try making a reproducible example when enlisting help from others: https://reprex.tidyverse.org/